---
title: "Omega sample with NIR, RAMAN"
subtitle: "Report Bin302 High throughput phenotyping for smart farming 2021"
author: "Jisoo Park"
date: "Last compiled date is `r format(Sys.Date())`"
output: 
  html_document:
    code_folding: hide
    fig_height: 6
    fig_width: 10
    toc: yes
    toc_depth: 4
    toc_float: yes
  # pdf_document:
  #   number_sections: true
  #   fig_width: 7
  #   fig_height: 6
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
Sys.setlocale("LC_TIME", "C")
options(scipen = 100000)
```

```{r libraries, include=FALSE}
suppressMessages({
  library(readr)      # read file
  library(tidyverse)  # data manipulation
  library(data.table) # data handling
  library(ggplot2);theme_set(theme_minimal())
  library(ggpubr)     # multiple plots in one figure
})
```

## Introduction
* Raman spectroscopy
* NIR
* Omega3 and Omega6, Pigment

## Problem statement 
NIR, RAMAN data sets have too many variables so it is good data to test a PCA, PCR, and PLSR

* PCA -> could be found the elbow point? If so, how many variables can be reduced
* PCR, PLSR -> comparison between RAMAN VS NIR
* could be segment?

- Many Possibilities for PLSR models comparing NIR and Raman for a phenotype
- Possibilities to compare Machine learning methods of prediction with PLSR for either 
NIR or RAMAN

the main problem of this analysis is I have no idea what is raman and nir...

## Description of data 

```{r read_datasets, message=FALSE}
Omega <- readr::read_csv("Omega_Assignment.csv")
NIR <- readr::read_csv("NIR_Assignment.csv")
RAMAN <- readr::read_csv("Raman_Assignment.csv")
```

This data set contains Raman, NIR and Omega 3 fatty acids composition, Omega 6 fatty acid composition and pigment of the salmon fillet in the same 200 fish.

Each data sets description are as below;

- `Omega_Assignment`:
  - n: Unique ID of fish
  - Omaga 3:
  - Omega 6:
  - pigment:

- `NIR_Assignment`:
  - n: Unique ID of fish
  - 1151-2499: wavelengths

- `Raman_Assighment`:
  - n: Unique ID of fish
  - x500-x1800: Raman shift
  
### Exploratory Data Analysis

```{r omega3_omega6}

Omega %>% 
  select(-n) %>% 
  cor()

Omega %>% 
  ggplot(aes(x = Omega3, y = Omega6)) + 
  geom_point() +
  geom_smooth(method = "lm", se = FALSE, 
              formula = "y ~ x") +
  scale_x_continuous(limits = c(15, 21),
                     breaks = c(seq(15, 21, by = 1))) +
  scale_y_continuous(limits = c(10, 15)) + 
  labs(title = "correlation between Omega3 and Omega 6",
       subtitle = paste0("corr: ", round(-0.59416308, 4)))

```


## Methods/Models tested

## Results – comparisons or benchmark 

## Conclusion
Implications or recommendations 

## References
